'''
Hidden Story:
    A long the storys and paths the parties travels there will be pictures in discreet locations of the major Houses in the region.
    The major houses all have their own unique storylines that will give the party access to the pictures, though these pictures will not be obvious in all occasions.
    The map of the area looks normal up front but within the map of the region are hidden symbols within each area and even a combination of symbols that join together into a greater symbolism. The Clown/Jester/Joker/Comedian/Trickster(satyr)/ManyFacedGod always is watching, if you anger it. It will attack, party can't kill it, can only get it to run away. It is the puppetmaster that controls what it wants, it mostly leaves the Houses to whatever they want to do, but if a House tries to do something that actively goes against it or causes too much information, it won't hesitate to take retribution.

Houses:
    The Crown - The Royal Family -
    The Coin - The Banking Clan -
    The Chalice - Priests of The White Flame (this is name can change) -
    The Sword - Bounty Hunters Guild -
    The Alembic - The Trade Council -
    The Scales - The High Courts - 

win spirit fights:
    -The feel like they have just seen a glimpse of the future, ominious darkness.
    -gain some xp
    -gain token representing image, useful later (potentially useful to show weakness of other entity or versions of boss), tokens have no checks (seem like just plain tokens)
    -potential value (low to high) depending on vendor

characters who die during spirit fights:
    -cursed with -1 to main stat (permenant NOT REMOVABLE)
    -stacks (upto -6 on main stat)(permenant NOT REMOVABLE)
    -wake up from bad nightmare, seem exhausted (lose short rests)
    -curse isn't visible, no warning, or indicator, just minus to stat
    -displayed minor debuff, -2 to random random proficiency (semi-permenant)

semi-permenant debuff removal:
    special questline or interaction to remove these proficiency debuffs, probably unique to each different art fight

Events:
Different checks:
 - perception & investigation all have levels
 - bonus stat checks dependent on specific depiction
 - high rolls required for unique flavor information (15+ probably)
6 pictures or depictions: 
    The Crown - jester - history, insight 
    1) Kings Court, artist unknown, oil painting
        perception: 1-3, just a picture of a kings court dinner nothing unique
        perception: 4-7, additionally you see everyone seems to be having a good time
        perception: 8-10, additionally you notice everyone is smiling, but something feels a bit off but you can't figure out why
        perception: 11-13, additionally, you notice that while everyone is smiling everyones eyes look sad
        perception: 14-16, additionally, you notice that king and queens throats are crimson like recently cut
        perception: 17-19, additionally, you notice the queen is holding a knife in one hand with blood on it, and her other hand seems to be holding a goblet out towards the center of the room
        perception: 20, additionally, you notice everyones eyes are focused on the jester, also you notice that there seems to be blood dripping from the table and instruments as well. 
                    Also, your eyes are drawn to the jester and you notice that it appears that he is facing directly at you, and as you move around the room he seems to follow you.
    The Coin - joker - CHA(Poker Strategy), WIS(Card Games)
    2) The Gamble, artist unknown, oil painting
        perception: 1-3, just a picture of 5 people playing a card game
        perception: 4-7, additionally you notice that each player has two cards in their hand and their are 3 on the table
        perception: 8-10, additionally you notice that each player has their other hand on a weapon, some blades and some guns
        perception: 11-13, additionally you can notice the hands of the two players one player has a 10,9 and the other player has a joker,10. The three cards on the table are 8,7,6.
        perception: 14-16, additionally you notice the player with the joker has a smurk on his face and his other hand has the hammer pulled back on his gun.
        perception: 17-19, additionally, you notice that the joker on card seems to be coming out of the card like its crawling out of the card.
        perception: 20, additionally you notice that each of the players at the table seem to be in a state of decay, and that the joker appears to be staring at you and watching where you are moving. 
    The Chalice - trickster - religion, medicine 
    3) Savior's Glass, artist unknown, stain-glass
        perception: 1-3, a pretty stain-glass window with vibrant colors
        perception: 4-7, additionally you notice there are some shapes, a shape on the left kind of large ball like shape, small shape in the middle, a tall and skinny rectangular shape on the right, and a bunch of different color shapes around the edges.
        perception: 8-10, additionally you notice that the shape on the left looks like a person kneeling, the shape on the right looks like a person standing with some sort of head ornament.
        perception: 11-13, additionally you can notice the shape in the middle is a golden cup or chalice that appears to be handed from the right to the left person. Also the head ornament is actually a halo, and the person on the right has wings.
        perception: 14-16, additionally you notice the shapes around the edges look more like small creatures, trying to reach toward the kneeling person. 
        perception: 17-19, additionally, you notice that there appears to be a large creature (satyr) behind the person/angel on the right. It looks a bit like the creature is actually manipulating the person.
        perception: 20, additionally you notice that the satyr(trickster) appears to be looking at you. Also you notice these small slivers of glass that appear to stick out of the stain glass, which you can only really see from side angles. These slivers seem to come from the creature and wrap around the arms of the person on the right and almost looks like its hand is wrapped around the chalice too.         
    The Sword - clown - survival, nature
    4) Hunted Hunter Hunting, artist unknown, tapestry
        perception: 1-3, just a tapestry of a man out in a forest.
        perception: 4-7, additionally you notice that the man is a hunter with some weapons.
        perception: 8-10, additionally you notice that the hunter seems to be chasing some animals
        perception: 11-13, additionally you see that there is another small person on the edge of the tapestry that appears to be a bit goofy looking carrying a sword bigger than itself.
        perception: 14-16, additionally you notice the hunters face actually looks scared and is looking back at the small person at the edge. You also notice that the small person looks a bit like a clown, silly hat, puffy clothes and silly make up on its face.
        perception: 17-19, additionally, the clowns face seems to be looking out at you. Also notice that the animals that looked previously to be chased by the hunter are actually laughing at the hunter.
        perception: 20, additionally you notice that the clowns eyes seem to follow you as you look around the tapestry, you also notice that the swords edge seems to be weaved from a glistening metalic fiber, you also notice that the fibers of the tapestry as you look at it longer and longer almost appear to be made out what they represent grass is made of grass, fabrics seem to feel like clothing, the animals fur appear to be the fur of the representative animal, and ever more bizarre the skin of the hunter looks like actual human skin.
    The Alembic - comedian - medicine, nature
    5) , artist unknown, set of drawings
        perception: 1-3, 
        perception: 4-7, 
        perception: 8-10, 
        perception: 11-13, 
        perception: 14-16, 
        perception: 17-19, 
        perception: 20, 
    The Scales - many-faced-god - arcana, religous
    6) Judgement, artist unknown, statue mural
        perception: 1-3, a large mural carved into the wall with what looks like a large battle.
        perception: 4-7, additionally you notice that the mural is broken up into 2 sides, charging towards each other with a giant figure in the middle, the entire mural is shaped like a mountain with the middle thing going from the bottom to the top.
        perception: 8-10, additionally you notice that the statue in the middle has 4 arms outstretched, and seems to have multiple heads sprouting out from the neck region, total count is unknown.
        perception: 11-13, you begin to notice that the forces on the battlefield are not fighting or looking at each other but are more focused towards the many-faced-god.
        perception: 14-16, additionally you notice that each of the faces on the god have a different expression, some have head garments, others hair, but each face appears to be unique.
        perception: 17-19, additionally, you notice that as you start looking around at all the different parts of the mural it always appears that at least one if not many of the heads are watching you.
        perception: 20, additionally you notice that the mural seems to be moving or alive, and there is a faint sound of moaning or crying out coming from the people on the battlefield.

'''